Anonymous provision of services via blockchain

### 2022-03-08 access.tex
grammarly fixes

\begin{keywords}
fair-exchange, blockchain, anonymity,  physical delivery, services
\end{keywords}

@@

Important individuals like top government, influencers, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position, or can be used for blackmailing.

The guarantee of the privacy of the data is often based merely on trust assumptions and the security of IT system. However, most of the SP does not need personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.

It would be desirable for the user to keep its identity private while the service provider still provides its services. This could lead to reduced trust that users have to put on SP and less responsibility borne by SP.

There is some services that would benefit from anonymous services, some examples are:
\begin{itemize}
    \item Patients willing to take a 
    test for drug, venereal diseases, paternity etc. have a strong incentive to keep the whole procedure private. Merely the fact that they took the test without exposing the result is suggestive enough to act as a premise in case of a conflict.

@@

Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorized actor (both curious employee, and malicious attacker).

Our protocol allows taking such tests anonymously and therefore getting
rid of the strong trust assumption put on the laboratories and their IT
systems.
\item People willing to take business activities that may be risky % or not yet fully legislated, 
may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.

By exposing our identity to the lawyer, we trust that he won't use that
information for harmful actions.

Our protocol would allow taking such advice anonymously, and therefore
getting rid of the strong trust assumption put on the lawyers and their IT systems.
\end{itemize}

@@

In case of dispute, either due to exceeding deadlines or providing
incorrect result, the customer can disclose the whole interaction and
prove to justice (police or court) the misbehavior of the service 
provider.
%JS a np automatyczny zwrot środków?
%SP to wymagałoby wprowadzenie depozytu co bardzo komplikuje cały system. Co więcej miałoby to sens tylko wtedy gdyby użyć "zdecentralizowanych sądów" (Future Work/Justice).

To achieve these objectives we use:
\begin{itemize}
    \item Privacy-preserving blockchain, to allow customers anonymously pay for the services.
    \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party.
    \item Content-addressable peer-to-peer storage network, to provide results to customers. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption: to encrypt and decrypt results published on public networks.
        \item Digital signatures: To achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

We observe that the issue of anonymous service provision can be seen as a problem of fair-exchange where parties exchange some goods in a fairly manner, i.e., either both parties obtain the goods, or they both obtain nothing.

In our case, the customer is exchanging with the SP cryptocurrency and materials for the result of a service.

%\paragraph{Contributions}
We contribute to the field of fair-exchanges by proposing a simple,
 practical, and anonymous protocol that does not rely on centralized trusted-third party, but on decentralized blockchain and
distributed content-addressable storage network.

@@

\begin{itemize}
\item Anonymity:
throughout the whole transaction, the customer stays anonymous to all external observers.
\item Fairness:
at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in the worst position.
\item Dispute resolution: at each step of the protocol the customer can start a dispute and win the case if and only if the SP misbehaved.

\item TTP-less: 
our protocol does not rely on a trusted-third party to conduct transactions in fairly manner. Only in case of dispute   the centralized justice is involved (the justice decentralization is discussed in Section ~\ref{sec:future-work}.
\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
\end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge we
are the first to propose a system that satisfies all five properties
stated above using blockchain technology. Especially anonymity and physical materials delivery, are
properties that were rarely addressed together, and if so, the protocol
based on TTP, and strong and impractical assumptions on banking system~\cite{birjoveanu2015anonymity}, or didn't address the conflict
between parties~\cite{altawy2017lelantos}.

Our protocol can potentially enable a variety of services that for many
customers based on unacceptable trust assumptions to the SP.

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In Section~\ref{sec:related-works} we briefly review related works. 
Section~\ref{sec:building-blocks} explains the background related to fair-exchanges, blockchain, anonymity and confidentiality, and storage network. 
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
Section~\ref{sec:future-work} discuss possible improvements. 
Finally, Section~\ref{sec:conclusion} concludes the paper.

@@

\subsection{Fair-exchange and blockchain}
The idea of certified mail is simple, neither the sender can deny sending the mail, nor the receiver can deny receiving it. As the service is widely used in paper world, achieving it for e-mails haven't meet the agreement across scientific community for over 40 years. The main reason was the dependency of TTP, which significantly reduce the performance, security, and robustness of such protocols. The protocols that do not use TTP struggle with high computation and communication overhead.

Authors of ~\cite{hinarejos2019solution} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation), which acts as a secure, verifiable, and decentralized TTP.

The idea behind certified e-mails and any other fair-exchange protocol is following:
\begin{enumerate}
    \item The sender sends encrypted and signed message to the receiver.
    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
    \item The sender publish on blockchain (or TTP in general) a proof of delivery and the decryption key.
    \item The receiver decrypts the encrypted message using the published decryption key.
\end{enumerate}

The non-repudiation requirement is achieved by the receiver sending the proof of delivery prior having access to the decrypted message. And the sender publishing the decription key together with the proof of delivery on blockchain (or TTP) so that the receiver can not deny both receiving the message and having access to decryption key, because it is publicly available.

The protocol also handles confidentiality — the encryption key used to encrypt and then decrypt the message is encrypted using the receiver's public key, so the key is never published in raw form.
Also, the protocol supports timeliness, meaning that the transaction is always finalized in a finite time.

In this case, the role of blockchain is to attest the public existence of decryption key at a particular point of time.

\subsection{Fair-exchange, anonymity, and physical products delivery} 
\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}

Authors of~\cite{birjoveanu2015anonymity} proposed a
fair-exchange of physical products and electronic payment protocol that
guarantee both customer and merchant anonymity. They achieve it by
introducing online trusted third parties that validate coins and provide
fair exchange guarantees.

The anonymity is ensured by assuming the existence of a source cabinet
(SC) and delivery cabinet (DC), and a trusted delivery agent who take
a product from a source cabinet and provide it to a destination cabinet.
Both cabinets provide access to the product by passwords to conceal
the identity of the customer and the merchant. To avoid identity disclosure
of customers and merchants, the access to the product is provided by
passwords.

@@

\begin{enumerate}
    \item Both parties agree on the purchase details.
    \item The customer buys a digital coin from his bank and validates it with the TTP.
    \item The customer sends to the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
    \item The merchant post the product to the source cabinet.
    \item Delivery agent collects the product from the source cabinet and posts it to the delivery cabinet.
    \item Customer collects the product from the delivery cabinet using a password.
    \item The customer checks if the product is the ordered one.
    \begin{itemize}
    \item[-] if yes 
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the customer sends the acknowledge to the delivery cabinet and decryption key to the merchant.
        \item The merchant redeem the coins from the bank.
        \end{enumerate}
    \item[-] if no
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP. 
        \item the dispute is settled via TTP, optionally letting each party reveal its identity.
    \end{enumerate}
    \end{itemize}
\end{enumerate}
\endgroup

Yet, the fair-exchange properties are achieved by strong assumptions.
Namely,

\begin{itemize}
    \item the TTP does not misbehave or collude with any party. 
    \item The customer's and merchant's banks enable confidential transactions and both share commit-buffer where the value is locked until the transaction is finished.   
    \item All banks maintain a global list of coin's serial numbers to prevent double-spending problems. 
    \item The source cabinet and delivery cabinet exist, and in both the product access is protected by a password.
    \item Delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute. 
    \item There exists a trusted delivery agent.
    \item Communication channels between parties provide anonymity.
\end{itemize}

@@

Themis~\cite{meng2019themis} is a fair-exchange
protocol, which uses blockchain instead of TTP. It provides escrow
services for secure exchanging between cryptocurrencies and digital goods, and a decentralized dispute resolution system for resolving conflicts.

Two parties say Alice and Bob, can create an escrow by generating
2-of-2 (not 2-of-3 as it is other TTP-based systems) threshold account
using Thresh-Key-Gen protocol. Alice and Bob generate secret keys
\(x_A\) and \(x_B\) accordingly, the shared account public key becomes
\(y = g^{x_A+x_B}\); only the access to both Alice's and Bob's secrets
grants access to the shared account.

Then, both Alice and Bob, take their keys, and split them into
\(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
\(n\) is the number of mediators that participate in the decentralized
network and \(t+1\) becomes the threshold of a sufficient number of
mediators that can reconstruct the secret key.

@@

The escrow is secure as long as \(t+1\) of mediators does not collude,
which would let them recreate both \(x_A\) and \(x_B\). Also, to ensure
that parties are exchanging real key shares, they also send a witnesses
generated with Feldman VSS scheme and zero-knowledge proofs to guarantee
the consistency between witnesses and key shares.

@@

The honesty of mediators is achieved by the monetary incentivization and
reputation system.

@@

Lelanros~\cite{altawy2017lelantos} is a blockchain-based anonymous
physical delivery system. The anonymity is achieved by employing ToR's
onion routing to connect physical delivery providers. The whole route
from merchant to a customer is split into multiple steps, and each step is
undertaken by the different randomly selected delivery providers. As long as
the delivery providers do not collude, a merchant can not learn both
the identity and destination address of the customer.

@@

However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see Section~\ref{sec:pseudo-anon}). Also, the protocol does not cover the case of dispute between the parties.

%JS moze\section{Building Blocks}
%SB Dla mnie idealnie.
\section{Building Blocks}\label{sec:building-blocks}

\subsection{Dispute resolution system}

@@

The vision of smart contracts was to replace the legal contract with
programmable and autonomous contracts. The specifications of the contract
were encompassed in the code, hence the slogan ``code as a law''. Yet,
the blockchain paradigm has its limitations. It can assure the
correctness of data existing on the blockchain. The problem arises in
the contact between blockchain and the real world. When we want the smart
contract to make a decision based on some input from outside the
blockchain. We move a lot of trust assumptions on the data providers.
The technique of providing real-world data to the blockchain is called
oracle. Oracle provides data based on a decentralized network of mediators,
therefore the trust is also decentralized.

Some oracles provide the data like weather, soccer match result, stock
price, train delay, election results, others---and they are the ones we
are interested in---provide the settlement of a submitted dispute.

Themis~\cite{meng2019themis} besides providing fair-exchange protocol,
also offers a semi-autonomous decentralized dispute resolution system,
which complies with the web3 postulates of a decentralized web. Themis
resolve disputes by a set of voluntary anonymous mediators participating
in voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivization and reputation
system.

Kleros~\cite{lesaege2018kleros} is a smart contract deployed on
Ethereum platform mimics in a decentralized and autonomous way how
the court works in real life. In Kleros, every process of a dispute like
gathering evidence, selecting jurors, rewarding the winning party is 
automated by a set of smart contracts. Similar to Themis, the honesty
of the agents voting in a case is achieved by game-theoretical economic
incentives.

Such decentralised, voluntary, and anonymous dispute resolution system
might work for simple contracts violation like eBay seller sending
broken or wrong product, or Airbnb apartment being not adequate to the
photos in the offer. However it's hard to realise such decentralised
evaluation of quality of heath or legal services when expertise and
privacy concerns are taken into an account. Therefore, in our protocol
we take the more conservative approach and resolve disputes using local
justice system (police, court, etc.).

Possible directions toward semi-autonomous decentralised resolution
system are discussed in Section ~\ref{sec:future-work}.

@@

In case of dispute, the customer can prove to justice (police, court, etc.) convincing evidence for the honesty of the customer and misbehavior of the SP. 
Because the customer is anonymous the SP can not start a dispute---there is no means to identify the customer.

To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantageous position, therefore he has no reason to start a dispute. The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the case.

Abstracting from the services the SP is providing, in case of a dispute each party should be able to prove its honest behavior. We introduce three proofs that should be disclosed to justice in case of a dispute:

\begin{enumerate}
    \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it. It consists of the current time; deadline to pay for the transaction; deadline to provide a result of the service; randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation. The formal definition of the $\mathrm{PoD}$ is presented in Section ~\ref{proof-of-delivery}.

    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction, at a certain time. The actual implementation depends on the particular cryptocurrency and is discussed further Section~\ref{payment-for-services}.

    \item Proof of provision ($\mathrm{PoP}$) is proof that the SP published the result at a certain time. It defends the SP in case the customer unjustly starts a dispute after the result have been published. It consists of a content identifier as specified in Section ~\ref{storage-network}; the value uniquely identifying the transaction previously generated in $\mathrm{PoD}$; the SP's signature guaranteeing authentication. The connection between $\mathrm{PoP}$ and the result is made by the content identifier (cid) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
\end{enumerate}

@@

By publishing the $\mathrm{PoP}$ on the blockchain, the SP can not falsify the time
at which the result has been provided, because the block creation time
proves that. Blockchain acts as a global clock that securely timestamps
everything that gets into the block, so the $\mathrm{PoP}$ that was included in a
block will be associated with the time when the block has been created. Moreover, since the blockchain is public, everyone (including justice) can be convinced that the SP indeed published the result at that time.

Without such a proof there would be no other means to settle the conflict between the customer claiming the result has not been published and the SP claiming the result has been published within the deadline.

Depending on the context the platform of achieving it is called bulletin board~\cite{achenbach2015improved} or message board~\cite{hinarejos2019solution} or trusted timestamping~\cite{gipp2015decentralized}. In this work we call it message board.

% Such functionallity is the easiest to achieve by the trusted third party that authoritatively tells what happened and when.

% Bitcoin introduced a way of decentralising not only the currency system,
% but also other similary working centralised trusted third parties
% including the message board.

We let keep the protocol general enough to 
be implemented using any of  
existing technology to provide message board service, with the
the assumption that it's decentralized and supports subscribing for the
upcoming proofs from a particular address.

@@

Privacy is a concept used in almost all kinds of social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambiguous definitions~\cite{smith2011information}. For our work we rely on more concrete definitions, i.e.~confidentality, and anonymity.

Confidentiality is the ability to hide the details of action from others. Or we can say, that the system guarantees confidentiality if for all observers everything they can say about the action is the fact that it happened and nothing more.

Anonymity is the ability to hide one identity from others. More precisely, the inability to correlate actions performed within the system with the identity of the user. Or we can say, that the system guarantees anonymity if for all observers the actions are equally likely to be associated with any user of the system. However, anonymity is a spectrum rather than a dichotomous classification. One method of quantifying the level of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}. It measures the user's anonymity by the number of other users from whom the user can not be distinguished. Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users. The larger \textit{k}, the higher anonymity.

Some techniques can be deployed on non-anonymous blockchains, the so-called mixers that gather together users into an \textit{anonymity set}, which then collude together to launder the transactions, in such a way that to an observer the likelihood of the sender of each transaction was equiprobable for any user from the anonymity set.

Some systems guarantee pseudonomity rather than anonymity. Pseudonomity allows users to hide their real identity behind the pseudonym. Despite the whole system being transparent and allowing linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret. This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity on most of the cryptocurrencies exchanges. This makes the anonymity of the user dependent on the security of the IT system. Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.

The relations between these terms are illustrated in the Figure~\ref{fig:anonymity-diagram1}.

\begin{figure}[h!]
\includegraphics[width=9cm]{anonymity-diagram.png}
\centering
\caption{Let us assume the Alice to be the customer willing to keep her identity private (anonymous) and Bob be the public SP. Alice controls two addresses 1 and 2, the connection between her real identity and the first address was compromised, and therefore the identification is possible, the connection between the second pseudonym is still unknown therefore anonymous. Alice takes two actions; the first one from the compromised address and the second one from anonymous one. The first action is confidential; therefore even though the psudonym has been compromised the action can not be associated with the Alice. The second action is transparent, therefore the Alice's anonymity is maintained as long as the connection to the second pseudonym is concealed.}

@@

The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and (ideally) unlikability, not via assumption that the connection between an address and the real identity is concealed.

>>>>

\begin{keywords}
Anonymity, blockchain, fair-exchange, physical delivery, privacy, services
\end{keywords}

@@

Important individuals like top government, influencers, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.

The privacy guarantee of the data is often based merely on trust assumptions and the security of the IT system. However, most SPs do not need personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.

It would be desirable for the user to keep its identity private while still receiving the service. This could lead to reduced trust that users have to put on SP and less responsibility borne by SP.

Examples of services that would benefit from the anonymity property are:
\begin{itemize}
    \item Patients willing to take a test for drugs, venereal diseases, paternity or steroids have a strong incentive to keep the whole procedure private. Merely the fact that they took the test—without exposing the result—is suggestive enough to act as a premise in case of a conflict.

@@

Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorized actor (both curious employee and malicious attacker).

Our protocol allows taking such tests anonymously, therefore eliminating the strong trust assumption put on the laboratories and their IT
systems.
\item People willing to take risky business activities may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.

By exposing our identity to the lawyer, we trust that he will not use that
information for harmful actions.

Our protocol would allow taking such advice anonymously, therefore eliminating the strong trust assumption put on the lawyers and their IT systems.
\end{itemize}

@@

In case of dispute, either due to exceeding deadlines or providing an  incorrect result, the customer can disclose the whole interaction and
prove to justice (police or court) the misbehaviour of the SP.

To achieve these objectives, we use:
\begin{itemize}
    \item Privacy-preserving blockchain, to allow customers anonymously pay for the services.
    \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party.
    \item Content-addressable peer-to-peer storage network to provide results to customers. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption: to encrypt and decrypt results published on public networks.
        \item Digital signatures: To achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.

In our case, the customer is exchanging with the SP cryptocurrency and materials for the result of the service.

%\paragraph{Contributions}
We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on the centralized trusted-third party but decentralized blockchain and
distributed content-addressable storage network.

@@

\begin{itemize}
\item Anonymity:
throughout the whole transaction, the customer stays anonymous to all external observers.
\item Fairness:
at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in the worst position.
\item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.

\item TTP-less: 
our protocol does not rely on a trusted third party to conduct transactions fairly. Only in case of dispute the centralized justice is involved (the justice decentralization is discussed in section ~\ref{sec:future-work}.
\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
\end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all five properties stated above using blockchain technology. Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and strong and impractical assumptions on banking system~\cite{birjoveanu2015anonymity} or did not address the conflict
between parties~\cite{altawy2017lelantos}.

Our protocol may enable various services currently based on unacceptable trust assumptions to the SP.

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we briefly review related works. 
Section~\ref{sec:building-blocks} explains the building blocks related to fair exchanges, blockchain, anonymity and confidentiality, and storage network. 
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
Section~\ref{sec:future-work} discuss possible improvements. 
Finally, section~\ref{sec:conclusion} concludes the paper.

@@

\subsection{Fair exchange and blockchain}
The idea of certified mail is simple, neither the sender can deny sending the mail, nor the receiver can deny receiving it. As the service is widely used in the paper world, achieving it for e-mails has not yet met the agreement across the scientific community. The main reason was the dependency of TTP, which significantly reduced the performance, security, and robustness of such protocols. The protocols that do not use TTP struggle with high computation and communication overhead.

Authors of ~\cite{hinarejos2019solution} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.

The idea behind certified e-mails and any other fair exchange protocols is following:
\begin{enumerate}
    \item The sender sends encrypted and signed message to the receiver.
    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
    \item The sender publishes proof of delivery and the decryption key on a blockchain (or TTP in general).
    \item The receiver decrypts the encrypted message using the published decryption key.
\end{enumerate}

The non-repudiation requirement is achieved by the receiver sending the proof of delivery prior to having access to the decrypted message and the sender publishing the decryption key together with the proof of delivery on the blockchain (or TTP) so that the receiver can deny neither receiving the message nor having access to the decryption key—because it is publicly available.

In this case, the role of blockchain is to certify the public existence of the decryption key at a certain time.

\subsection{Fair exchange, anonymity, and physical products delivery} 
\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}

Authors of~\cite{birjoveanu2015anonymity} proposed a
fair exchange of physical products and electronic payment protocol that
guarantee both customer and merchant anonymity. They achieve it by
introducing online trusted third parties that validate coins and provide
fair exchange guarantees.

The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take
a product from a source cabinet and provide it to a destination cabinet.
Both cabinets provide access to the product by passwords to conceal
the identity of the customer and the merchant.

@@

\begin{enumerate}
    \item Both parties agree on the purchase details.
    \item The customer buys a digital coin from his bank and validates it with the TTP.
    \item The customer sends the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
    \item The merchant post the product to the source cabinet.
    \item Delivery agent collects the product from the source cabinet and posts it to the delivery cabinet.
    \item Customer collects the product from the delivery cabinet using a password.
    \item The customer checks if the product is the ordered one.
    \begin{itemize}
    \item[-] if yes 
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the customer sends the acknowledge to the delivery cabinet and decryption key to the merchant.
        \item The merchant redeem the coins from the bank.
        \end{enumerate}
    \item[-] if no
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP. 
        \item the dispute is settled via TTP, optionally letting each party reveal its identity.
    \end{enumerate}
    \end{itemize}
\end{enumerate}
\endgroup

However, the protocol relies on strong assumptions to achieve fairness.
Namely,

\begin{itemize}
    \item the TTP does not misbehave or collude with any party. 
    \item The customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished.   
    \item All banks maintain a global list of coins' serial numbers to prevent double-spending problems. 
    \item The source cabinet and delivery cabinet exist, and in both, the product access is protected by a password.
    \item Delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute. 
    \item There exists a trusted delivery agent.
    \item Communication channels between parties provide anonymity.
\end{itemize}

@@

Themis~\cite{meng2019themis} is a fair exchange
protocol that uses blockchain instead of TTP. It provides an escrow
service for secure exchanging cryptocurrencies and digital goods. Also, it provides a decentralized dispute resolution system for resolving conflicts.

Two parties say, Alice and Bob, can create an escrow by generating
2-of-2 (not 2-of-3 as it is other TTP-based systems) threshold account
using Thresh-Key-Gen protocol. Alice and Bob generate secret keys
\(x_A\) and \(x_B\) accordingly, the shared account public key becomes
\(y = g^{x_A+x_B}\); only the access to both Alice's and Bob's secrets
grants access to the shared account.

Then, both Alice and Bob take their keys and split them into
\(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
\(n\) is the number of mediators that participate in the decentralized
network and \(t+1\) becomes the threshold of a sufficient number of mediators to reconstruct the secret key.

@@

The escrow is secure as long as \(t+1\) of mediators does not collude,
which would let them recreate both \(x_A\) and \(x_B\). To ensure
that parties exchange actual key shares, they send witnesses
generated with the Feldman VSS scheme and zero-knowledge proofs to guarantee the consistency between witnesses and key shares.

@@

The monetary incentivization and reputation system guarantee the honesty of mediators.

@@

Lelanros~\cite{altawy2017lelantos} is a blockchain-based anonymous
physical delivery system. The protocol achieves anonymity by employing onion routing (similar to the Tor network) to connect physical delivery providers. The whole route from a merchant to a customer is split into multiple steps, and each step is undertaken by the different randomly selected delivery providers. As long as the delivery providers do not collude, a merchant neither can learn the identity nor destination address of the customer.

@@

However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see Section~\ref{sec:pseudo-anon}). Also, the protocol does not cover the dispute between the parties.

\section{Building Blocks}\label{sec:building-blocks}
\subsection{Dispute resolution system}

@@

The vision of smart contracts was to replace the legal contract with
programmable and autonomous contracts. The smart contract code encompasses the contract's specifications, hence the slogan ``code as a law''.

Nevertheless, the blockchain paradigm has its limitations. Blockchain can assure the correctness of data existing only on the blockchain—the problem arises in the contact between blockchain and the real world when we want the smart contract to decide based on some input from outside the blockchain. The technique of providing real-world data to the blockchain is called oracle. Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized.

Some oracles provide the data like weather, soccer match result, stock
price, train delay, election results, others—and they are the ones we
are interested in—provide the settlement of a submitted dispute.

Themis~\cite{meng2019themis} besides providing fair exchange protocol,
also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web. Themis
resolve disputes by a set of voluntary anonymous mediators participating
in voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivization and reputation
system.

Kleros~\cite{lesaege2018kleros} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life. In Kleros, every process of a dispute like gathering evidence, selecting jurors, rewarding the winning party is automated by a set of smart contracts. Like Themis, the honesty of the agents voting in a case is achieved by game-theoretical economic incentives.

Such a decentralized, voluntary, and anonymous dispute resolution system might work for simple contracts violations like an eBay seller sending broken or wrong products or an Airbnb apartment being inadequate to the photos in the offer. However, it is hard to realize such decentralized evaluation of heath or legal services quality when expertise and privacy concerns are taken into account. Therefore, in our protocol, we take the more conservative approach and resolve disputes using local
justice system (police or court).

Possible directions toward semi-autonomous decentralized resolution
system are discussed in Section ~\ref{sec:future-work}.

@@

In case of dispute, the customer can prove to justice (police or court) convincing evidence for the honesty of the customer and misbehaviour of the SP. 
Because the customer is anonymous, the SP can not start a dispute---there is no means to identify the customer.

To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantageous position; therefore, he has no reason to start a dispute. On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.

Abstracting from the services the SP is providing, each party should be able to prove its honest behaviour in case of a dispute. We introduce three proofs that should be disclosed to justice in case of a dispute:

\begin{enumerate}
    \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it. It consists of the current time, the deadline to pay for the transaction, the deadline to provide a result of the service, randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation. The formal definition of the $\mathrm{PoD}$ is presented in Section ~\ref{proof-of-delivery}.

    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction at a certain time. The actual implementation depends on the particular cryptocurrency and is discussed further Section~\ref{payment-for-services}.

    \item Proof of provision ($\mathrm{PoP}$) is proof that the SP published the result at a certain time. It defends the SP in case the customer unjustly starts a dispute after the result has been published. It consists of a content identifier as specified in section ~\ref{storage-network}, the $\mathrm{nonce}$ uniquely identifying the transaction previously generated in $\mathrm{PoD}$, and the SP's signature guaranteeing authentication. The connection between $\mathrm{PoP}$ and the result is created by the content identifier ($\mathrm{cid}$) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
\end{enumerate}

@@

By publishing the $\mathrm{PoP}$ on the blockchain, the SP can not falsify the time at which the result has been provided because the block creation time proves that. Blockchain acts as a global clock that securely timestamps everything that gets into the block, so the $\mathrm{PoP}$ that was included in a block will be associated with the time when the block has been created. Moreover, since the blockchain is public, everyone (including justice) can be convinced that the SP indeed published the result at that time.

Without such proof, there would be no other means to settle the conflict between the customer claiming the result has not been published and the SP claiming the result has been published within the deadline.

Depending on the context the platform of achieving it is called bulletin board~\cite{achenbach2015improved} or message board~\cite{hinarejos2019solution} or trusted timestamping~\cite{gipp2015decentralized}. In this work, we call it a message board.

We keep the protocol general enough to be implemented using any existing technology to provide message board service, assuming it is decentralized and supports subscribing for the upcoming proofs from a particular address.

@@

Privacy is a concept used in almost all social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambiguous definitions~\cite{smith2011information}. For our work, we rely on more concrete definitions, i.e.~confidentality, and anonymity.

Confidentiality is the ability to hide the details of action from others. Alternatively, we can say that the system guarantees confidentiality if, for all observers, everything they can say about the action is the fact that it happened and nothing more.

Anonymity is the ability to hide one identity from others. More precisely, the inability to correlate actions performed within the system with the user's identity. Alternatively, we can say that the system guarantees anonymity if, for all observers, the actions are equally likely to be associated with any user of the system. However, anonymity is a spectrum rather than a dichotomous classification. One method of quantifying the level of anonymity is \textit{k}-anonymity proposed in~\cite{sweeney2002k}. It measures the user's anonymity by the number of other users from whom the user can not be distinguished. Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users; the larger \textit{k}, the higher anonymity.

Some anonymity techniques can be deployed on non-anonymous blockchains. The so-called mixers gather users into an \textit{anonymity set}, which then collude together to launder transactions in such a way that to an observer, the likelihood of the sender of each transaction is equiprobable for any user from the anonymity set.

Some systems guarantee pseudonymity rather than anonymity. Pseudonymity allows users to hide their real identity behind the pseudonym. Despite the whole system being transparent and allowing linking actions to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret. This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity to cryptocurrencies exchanges, making the user's anonymity dependent on the security of the IT system. Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.

The figure ~\ref{fig:anonymity-diagram1} ilustrate relations between these terms.

\begin{figure}[h!]
\includegraphics[width=9cm]{anonymity-diagram.png}
\centering
\caption{Let us assume Alice to be the customer willing to keep her identity anonymous and Bob to be the public SP. Alice controls two addresses, 1 and 2; the connection between her real identity and the first address has been compromised, and therefore the identification is possible; the connection between the second pseudonym is still unknown therefore anonymous. Alice takes two actions; the first one from the compromised address and the second one from the anonymous one. The first action is confidential; therefore, even though the pseudonym has been compromised, the action can not be associated with Alice. The second action is transparent; therefore, Alice maintain her anonymity as long as the connection to the second pseudonym is concealed.}

@@

The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and (ideally) unlikability, not via the assumption that the connection between an address (pseudonym) and the real identity is concealed.
